Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
added assumption 1

\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}

@@

It will also be useful to compute the derivative of $u_t$ with respect to time $t$ from the explicit form in equation (\ref{eq:riccati_ut_sol}):
\begin{equation}
\frac{d u_t}{dt} = \frac{\left(B (D^{u})^2 + 2 A^u D^{u} - C^{u} \right) \cdot \left(\delta_u^{+} - \delta_u^{-}\right)^2 e^{- (\delta_u^{+} - \delta_u^{-})(T-t) } }{\left[B D^{u}(1-e^{- (\delta_u^{+} - \delta_u^{-})(T-t)})   + \delta_u^{+}e^{- (\delta_u^{+} - \delta_u^{-})(T-t)}- \delta_u^{-}  \right]^2 }.
\label{eq:riccati_ut_sol_deriv}
\end{equation}
Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.

In the following propositions, based on assumption (\ref{eq:assumptions}) and the positivity of coefficients, we assume in addition that $b_1 > 0, D^{u} > 0, D^w > 0, D^{\eta} >0$ and the initial condition $\xi$ satisfies $\mathbb{E}(\xi) \neq 0$. These assumptions allow us to better understand the main ideas and techniques employed in the following propositions.

% proposition r to infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), then:
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From the assumption $q_T+\bar{q}_T(1-s_T)>0$, we have $D^{u,b_2}>0$. From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

@@

	%\textbf{Case 1:} when
	From the assumption:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC}{SC^{MKV}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

%proposition b_2 \to 0
\begin{proposition}
	Assume (\ref{eq:assumptions}). If $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{b_2\to 0} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

@@

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we derive that for any fixed $t \in [0,T]$:
	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
	It can also be shown that $\left| \bar{x}_t^{MFG,b_2}\right| \leq \vert \mathbb{E}(\xi) \vert e^{(b_1 + \bar{b}_1) T}$ for any $t \in [0,T]$ and $b_2 > 0$.

	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w \geq 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$. It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$. Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
	\begin{equation*}
	\lim_{b_2 \to 0} \Delta SC^{b_2} = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
	\end{equation*}

	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for small $b_2$ and for all $t \in[0,T]$:
	$$\lim_{b_2 \to 0}\eta_t^{b_2}=\left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }=:\eta_t^{b_2 \to 0}.$$

@@

% proposition b2 bar infinity
\begin{proposition}
	Assuming (\ref{eq:assumptions}). 
	If	$	\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
	\end{equation*}	
	When $\bar{b}_2$ tends to infinity, we always have:
	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
	\label{prop:b2bar}
\end{proposition}

\begin{proof}	
	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Because $b_1 > 0$, we have $A^u < 0$. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
	\begin{equation*}
		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
	\end{equation*}

	Similarly, for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}w^{\bar{b}_2}_t=w^{\bar{b}_2 \to 0}_t$, and  $w^{\bar{b}_2}$ is uniformly bounded over $[0,T]$ for small enough $\bar{b}_2$. From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption on $\xi$, and by the bounded convergence theorem, we have for every $t \in [0,T]$:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG,\bar{b}_2} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{\bar{b}_2 \to 0}u^{\bar{b}_2 \to 0}_s) ds} =: \bar{x}^{MFG,\bar{b}_2 \to 0}_t\neq 0.$$
	Moreover, $\bar{x}^{MFG,\bar{b}_2}$ is uniformly bounded for all $\bar{b}_2<\bar{b}^*_2$ and for all $t \in [0,T]$. From the non-negativity of $u_t$, we have:
	$$ \left\vert \bar{x}^{MFG,\bar{b}_2}_t \right\vert \leq \left\vert \mathbb{E}(\xi) \right\vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T], \ \forall \bar{b}_2<\bar{b}^*_2. $$

	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$

>>>>

\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

@@

It will also be useful to compute the derivative of $u_t$ with respect to time $t$ from the explicit form in equation (\ref{eq:riccati_ut_sol}):
\begin{equation}
\frac{d u_t}{dt} = \frac{\left(B (D^{u})^2 + 2 A^u D^{u} - C^{u} \right) \cdot \left(\delta_u^{+} - \delta_u^{-}\right)^2 e^{- (\delta_u^{+} - \delta_u^{-})(T-t) } }{\left[B D^{u}(1-e^{- (\delta_u^{+} - \delta_u^{-})(T-t)})   + \delta_u^{+}e^{- (\delta_u^{+} - \delta_u^{-})(T-t)}- \delta_u^{-}  \right]^2 }.
\label{eq:riccati_ut_sol_deriv}
\end{equation}
Note that $u_t$ is increasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}>0$, and likewise, decreasing if $B (D^{u})^2 + 2 A^u D^{u} - C^{u}<0$.\\

In the following propositions, we utilize the following assumption.	
\begin{assumption}\label{assumption}
	Assume (\ref{eq:assumptions}). In addition, assume: $b_1 > 0$, $D^{u} > 0$, $D^w > 0$, $D^{\eta} >0$ and the initial condition satisfies $\mathbb{E}(\xi) \neq 0$.
\end{assumption}

% proposition r to infty
\begin{proposition}
	Assuming assumption \ref{assumption}, then:
	\begin{equation*}
			\lim_{r \to \infty} PoA = 1 \qquad \text{and} \qquad
			\lim_{\bar{r} \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:r_bar_r}
\end{proposition}
\begin{proof}
	First, we consider $r \to \infty$. For every given $r >0$, we have existence and uniqueness of the solutions $u^{r}_t$, $w^{r}_t$ and $\eta^{r}_t$ to the scalar Riccati equations (\ref{eq:riccati_ut})-(\ref{eq:riccati_etat}). Note that we have added the superscript $r$ to emphasize the dependence on this parameter.

@@

% proposition b_2 to \infty
\begin{proposition}
	Assuming assumption \ref{assumption}, and if
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})} =\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}
\begin{proof}
	When $b_2 \to \infty$, we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}, \quad	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} >0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^{w}, C^w, D^w), (A^{\eta}, C^{\eta}, D^{\eta})$ are independent of  $b_2$. Moreover, we notice that:
	\begin{equation*}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} = -\frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{(A^u)^2}{(b_2+\bar{b}_2)^2}+\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} } \xrightarrow[b_2 \to \infty]{} \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}.
	\end{equation*}
	and thus, $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$.
	From equation (\ref{eq:riccati_ut_sol}), for each $t \in[0,T)$, we deduce:
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_u.
	\end{IEEEeqnarray*}
	Idem, for all $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_w,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} },$$
	and
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r + \bar{r}) \cdot c_{\delta_{\eta}^{b_2 \to \infty}} =: c_\eta, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}}{r +\bar{r}} }.$$

@@

	%\textbf{Case 1:} when
	From the assumption:
	\begin{equation*}
	\frac{q+\bar{q}(1-s)}{r+\bar{r}(1-\bar{s})}=\frac{q+\bar{q}(1-s)^2}{r+\bar{r}(1-\bar{s})^2},
	\end{equation*}
	we have $c_{\delta_u^{b_2 \to \infty}}=c_{\delta_w^{b_2 \to \infty}}$ and therefore, $c_u = c_w =: c$. 
	We would like to show in this case that $\lim_{b_2 \to \infty} \frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} = 0$. Our approach is to split the interval $[0,T]$ into two parts: $[0,T/2]$ and $[T/2,T]$.	
	Since $v^{b_2}_t \geq 0$ for all $t\in [0,T]$, we have $SC^{MKV,b_2} \geq w_0^{b_2} (\mathbb{E}(\xi))^2$.	For the sake of simplicity, we denote $h_u(b_2,t) := (b_2 + \bar{b}_2) u_{t}^{b_2}$ and $h_w(b_2,t) := (b_2 + \bar{b}_2)w_t^{b_2}$. We have:
	\begin{equation}
	\begin{split}
		\frac{\Delta SC^{b_2}}{SC^{MKV,b_2}} &\leq \frac{1}{w_0^{b_2} \mathbb{E}(\xi)^2 } \left( B^{b_2} \int_{0}^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt + B^{b_2} \int_{\frac{T}{2}}^{T} (u_t^{b_2} - w_t^{b_2})^2 (\bar{x}_t^{MFG,b_2})^2 dt \right) \\ 
		&=  \frac{1}{(b_2 + \bar{b}_2) w_0^{b_2} } \left( I_1^{b_2} + I_2^{b_2} \right),
	\end{split}
	\label{eq:I_1_plus_I_2}
	\end{equation}
	where:
	\begin{IEEEeqnarray*}{rCl}
	I_1^{b_2} &=& \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_0^{\frac{T}{2}} (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -2B^{b_2} \int_0^{t} u_s^{b_2} ds 
	\right) dt \\
	&=& \frac{b_2 + \bar{b}_2}{r + \bar{r}(1-\bar{s})^2} \int_0^{\frac{T}{2}} [ h_u(b_2,t)- h_w(b_2,t) ]^2 \cdot e^{2(b_1 + \bar{b}_1)t} \exp \left( - \frac{2 (b_2 + \bar{b}_2)}{r+ \bar{r}(1-\bar{s})^2}  \int_0^t h_u(b_2,s) ds \right) dt, 
	\end{IEEEeqnarray*}
	and:
	$$
		I_2^{b_2} = \frac{(b_2 + \bar{b}_2)^3}{r + \bar{r}(1-\bar{s})^2}  \int_{\frac{T}{2}}^T (u_t^{b_2} - w_t^{b_2})^2 e^{2(b_1 + \bar{b}_1)t} \exp \left( -\frac{2 (b_2 + \bar{b}_2)}{r + \bar{r}(1-\bar{s})^2} \int_0^{t} h_u(b_2,s) ds \right) dt.
	$$

@@

%proposition b_2 \to 0
\begin{proposition}
	Assume assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{b_2\to 0} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

@@

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), the assumption $\mathbb{E}(\xi)\neq 0$, and by the bounded convergence theorem, we derive that for any fixed $t \in [0,T]$:
	$$\lim_{b_2 \to 0} \bar{x}_t^{MFG,b_2} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} \neq 0.$$
	It can also be shown that $\left| \bar{x}_t^{MFG,b_2}\right| \leq \vert \mathbb{E}(\xi) \vert e^{(b_1 + \bar{b}_1) T}$ for any $t \in [0,T]$ and $b_2 > 0$.

	Moreover, since $B^{b_2 \to 0}>0$, $B^{b_2 \to 0}C^w >0$, $B^{b_2\to 0}D^w > 0$, we have $\lim_{b_2 \to 0} w_t^{b_2}=:w_t^{b_2 \to 0}$, and $w_t^{b_2 \to 0}$ is strictly positive over $[0,T)$. It is easy to check that $w_t^{b_2}$ is also uniformly bounded over $[0,T]$ for small $b_2$. Hence, from Proposition \ref{prop:diff_SC} and the bounded convergence theorem, we deduce:
	\begin{equation*}
	\lim_{b_2 \to 0} \Delta SC^{b_2} = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
	\end{equation*}

	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} > 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for small $b_2$ and for all $t \in[0,T]$:
	$$\lim_{b_2 \to 0}\eta_t^{b_2}=\left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }=:\eta_t^{b_2 \to 0}.$$

@@

% proposition b2 bar infinity
\begin{proposition}
	Assuming assumption \ref{assumption}, then:
	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
	Furthermore, if	$\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
	\end{equation*}	
	\label{prop:b2bar}
\end{proposition}

\begin{proof}
	% case when b2 bar \to infty
	\textbf{Case 1:} When $\bar{b}_2 \to \infty$,  we have:
	\begin{equation*}
	\begin{array}{l}
	\lambda^{\bar{b}_2} \to 0,\\
	B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0,
	\end{array}
	\end{equation*}
	and $A^{u}, (A^w,C^w,D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.
	Following the same technique used in Proposition \ref{prop:b2_to_infty}, we can show that:
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},
	\qquad
	\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm, \bar{b}_2}_w}{b_2 + \bar{b}_2} = \pm \sqrt{\frac{q+\bar{q}(1-s)^2}{r+ \bar{r}(1-\bar{s})^2}} =: \pm c_{\delta_w^{\bar{b}_2 \to \infty}},$$
	and, for all $0 \leq t < T$:
	\begin{equation*}
	\begin{array}{l}
	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta^{\bar{b}_2 \to \infty}_u} =: c_u, \\
	(b_2 + \bar{b}_2) w_t^{\bar{b}_2} \xrightarrow[\bar{b}_2 \to \infty]{} (r + \bar{r}(1-\bar{s}^2) ) \cdot c_{\delta_w^{\bar{b}_2\to \infty}} =: c_w.
	\end{array}
	\end{equation*}
